---
title: "R Lidar Workshop"
author: "Jacob"
date: "2023-08-06"
output: html_document
---

```{r eval=FALSE, include=FALSE}
install.packages("data.table")

install.packages("dbscan")

install.packages("deldir")

install.packages("dplyr")

install.packages("geometry")

install.packages("lidR")

install.packages("sf")

install.packages("shiny")

install.packages("shinyFiles")

install.packages("shinyjs")

install.packages("terra")

install.packages("RCSF")

install.packages("randomForest")

```

```{r}
library(phyloseq)
library(data.table)
library(dbscan)
library(deldir)
library(dplyr)
library(geometry)
library(lidR)
library(sf)
library(shiny)
library(shinyFiles)
library(shinyjs)
library(terra)
library(RCSF)
library(randomForest)
library(FPCALSpackage)
```

here are six tools available through the
tabs in the
GUI, these are:
1.
Pre
-
processing
tasks
;
2.
Plot
-
area scale metric estimation of basic metrics and extraction of model covariates;
3.
Stand
-
area scale estimation of basic metric
s;
4.
Large area scale estimation of basic metrics;
5.
Individual tree crown delineation and estimation of tree size metrics;
6.
Satellite leaf area index calculation.
The following
will describe the
basic function of each of these tabs. We recommend you use the Rs
tudio
API when using this package.



#Launching the GUI program

```{r}
fpc.lidar.app()
```

